Smart Drill-Down

### 2015-10-11 TableSummarization/Paper/exp.tex
changes

Figure~\ref{fig:minSS_speed}(a) shows that sampling gives us noticeable time savings. The percent error decreases approximately as $\frac{1}{\sqrt{minSS}}$, which is again expected because the standard deviation of estimated $Count$ is approximately inversely proportional to the square root of sample size.

@@

\subsubsection{Scaling properties of our algorithms}
The computation time for a smart drill-down is linear in both the table size $|T|$ and in parameter $minSS$. That is, the runtime can be written as $a \times |T| + b \times minSS$ where $a$ and $b$ are constants. In the worst-case wherer we cannot form a sample from main memory and need to re-create a sample, $a$ stands for the time taken to read data from hard disk. That is, $a \times |T|$ is the time taken to make a single pass over the table on hard disk. The constant $b$ is bigger than $a$, because BRS makes multiple passes over the sample, while creating a sample only requires a single pass over the table.

When the $|T|$ is small, the runtme is dominated by the $b \times minSS$ term, as seen for the Marketing Dataset in Figure~\ref{fig:minSS_speed}(a). When $|T|$ is large relative to $minSS$, like for the Census Dataset, the runtime is dominated by the $a \times |T|$ term (this is when we need to create a fresh sample from hard disk). When we have a few million tuples, we only require a few seconds. But if the dataset consisted of billions of tuples, the process of reading the table to create a sample could itself take a very long time. To counteract this, we could preprocess the dataset by down-sampling it to only a million tuples, and perform the summarization on the million tuple sample (which also effectively summarizes the billion tuple table).

>>>>

\agp{Figure~\ref{fig:minSS_speed}(a) shows that sampling gives us noticeable time savings. The percent error decreases approximately as $\frac{1}{\sqrt{minSS}}$, which is again expected because the standard deviation of estimated $Count$ is approximately inversely proportional to the square root of sample size.}

@@

\agp{
\subsubsection{Scaling properties of our algorithms}
The computation time for a smart drill-down is linear in both the table size $|T|$ and in parameter $minSS$. That is, the runtime can be written as $a \times |T| + b \times minSS$ where $a$ and $b$ are constants. In the worst-case wherer we cannot form a sample from main memory and need to re-create a sample, $a$ stands for the time taken to read data from hard disk. That is, $a \times |T|$ is the time taken to make a single pass over the table on hard disk. The constant $b$ is bigger than $a$, because BRS makes multiple passes over the sample, while creating a sample only requires a single pass over the table.

When the $|T|$ is small, the runtme is dominated by the $b \times minSS$ term, as seen for the Marketing Dataset in Figure~\ref{fig:minSS_speed}(a). When $|T|$ is large relative to $minSS$, like for the Census Dataset, the runtime is dominated by the $a \times |T|$ term (this is when we need to create a fresh sample from hard disk). When we have a few million tuples, we only require a few seconds. But if the dataset consisted of billions of tuples, the process of reading the table to create a sample could itself take a very long time. To counteract this, we could preprocess the dataset by down-sampling it to only a million tuples, and perform the summarization on the million tuple sample (which also effectively summarizes the billion tuple table).
}

### 2015-10-11 TableSummarization/Paper/sampling.tex
changes

We are given a memory capacity or budget $M$, and a minimum sample size $minSS$ (both specified by the user).
The parameter $minSS$ is the minimum number of sample tuples needed
such that we can use the sample in memory 
instead of having to resort to the entire table stored
on hard disk. 
This parameter determines how accurate our count estimates will be, and also
how quickly we can return results to the user.

>>>>

We are given a memory capacity or budget $M$, and a minimum sample size $minSS$ (both specified by the user). \agp{$M$ can simply be set to the actual available memory, while $minSS$ can easily be computed as a function of the desired estimation error.}
The parameter $minSS$ is the minimum number of sample tuples needed
such that we can use the sample in memory 
instead of having to resort to the entire table stored
on hard disk. 
This parameter determines how accurate our count estimates will be, and also
how quickly we can return results to the user. \agp{The count estimate error is proportional to $\sqrt{\frac{1}{minSS}}$ while runtime is proportional to $minSS$.}
